A Proposal for an Intuitionistic Fuzzy Inference System

### 2016-01-06 paper.tex
2/3 of the proposed method done

How a classic fuzzy set is represented as a ifs. How an intuitionistic
fuzzy set is represented in this work.

How the non-membership is going to affect the membership (show
formula). Present both examples (stating the parameters).

How the coa is calculated (show formula and plot). How the formula can
be contracted.

@@

\begin{figure}[!t]
  \centering
  \includegraphics[width=2.5in]{ifs}
  \caption{An Example of an Intuitionistic Fuzzy Set}
  \label{ifs}
\end{figure}

@@

@@

% i-membership
\begin{equation}
  i\mu_{A}(x) = (\nu_{A}(x) + \mu_{A}(x))\mu_{A}(x)
\end{equation}

>>>>

The method, for now, consists on the procedures and elements
necessary to construct a basic Intuitionistic Fuzzy Inference System
(IFIS). This design was completed in order to make comparisons against
classic Fuzzy Inference Systems (FISs), such as Type-1 FIS, Interval
Type-2 and General Type-2 FIS, and prove that
the design was viable and able to contribute to better results than
the classic FISs.

In many works, intuitionistic fuzzy sets (IFSs) are constructed by
hand, by interviewing experts who assign memberships and
non-memberships to each of the values of a set (such as in
\cite{davarzani2013novel}). This work proposes a convenient way of
creating an IFS, imitating many systems that use Gaussian
membership functions (MFs) to facilitate an expert the representation of a
fuzzy interpretation. An example of an IFS is depicted in
Fig. \ref{fs-as-ifs}. This IFS represents a classic fuzzy set, as it
satisfies (\ref{ifs-form}) and (\ref{fs-as-ifs-if}), by representing
the MF as the red line, and the non-membership
function (NMF) as the blue line. In order to contruct the NMF, one has
to rotate a normal Gaussian MF by 180˚, and this can be seen as the
complement of the fuzzy set corresponding to a Gaussian MF.

@@

Two convenient ways of modifying the NMF and
satisfy (\ref{intuitionistic-interval}) are as follows: 1) one can set
the mean and the standard deviation of the Gaussian functions to be
the same, and only vary the $height$ of the NMF,
as is depicted in Fig. \ref{ifs}; and 2) one can set different means and
standard deviations of the Gaussian membership and non-membership
functions, but the $height$ of the MF must be equal
to $h_{mf} = 1 - h_{nmf}$, as this ensures that
(\ref{intuitionistic-interval}) is satisfied. An example of the latter
case is shown in Fig. \ref{ifs-diff-mu-sd}. To clarify, the $height$
of the MF ($h_{mf}$) of an IFS is equal to $max(\mu(x))$, and the
$height$ of the NMF ($h_{nmf}$) of an IFS is equal to $max(\nu(x))$.

\begin{figure}[!t]
  \centering
  \includegraphics[width=2.5in]{ifs}
  \caption{An Example of an Intuitionistic Fuzzy Set - Same Mean and SD}
  \label{ifs}
\end{figure}

\begin{figure}[!t]
  \centering
  \includegraphics[width=2.5in]{ifs-diff-mu-sd}
  \caption{An Example of an Intuitionistic Fuzzy Set - Different Mean
    and SD}
  \label{ifs-diff-mu-sd}
\end{figure}

The first step in an inference process in a classic FIS (a flow chart
for the process in an IFIS is given in Fig. \ref{flow-chart}) is to
determine what membership corresponds to a given input, given a set of
MFs. This is straightforward in a classic FIS, as the
membership to each input is already established in the membership
fuzzy set. For an IFIS, this work proposes a method to determine a
membership given a MF and a NMF,
which is described in (\ref{imembership}), and receives the name of
$i\mu$ (intuitionistic membership).

\begin{figure}[!t]
  \centering
  \includegraphics[height=2.5in]{proposed-method-flow-chart}
  \caption{Proposed Method Flow Chart}
  \label{flow-chart}
\end{figure}

% i-membership
\begin{equation}
  \label{imembership}
  i\mu_{A}(x) = (\nu_{A}(x) + \mu_{A}(x))\mu_{A}(x)
\end{equation}

A comparison of a MF (red line) against an intuitionistic
membership function (blueline) is shown in Fig.
\ref{if-membership}. The parameters for both the MF and NMF are $\mu =
50$ and $SD = 15$, but the $height$ for the NMF is set at $0.5$. This
results in an intuitionistic MF that appears to have the same mean,
but a smaller standard deviation. A more elaborated example is shown
in Fig. \ref{if-membership-drastic}, where the parameters of the MF
are $\mu = 50$, $SD = 15$ and $h = 0.8$, and the parameters of the NMF
are $\mu = 30$, $SD = 20$ and $h = 0.2$. As can be noted, the
indeterminancy ($\pi$) is high in this example, which results in a
smaller $SD$ for the intuitionistic MF. Moreover, the difference in
means and standard deviations generates a change of the mean for the
intuitionistic MF.

@@

The next step in the inference process is to perform an $\alpha$-cut
on the associated consequents to the antecedents that are activated by
the inputs. In a classic FIS, this process is straightforward, as the
memeberships in a fuzzy set representing a consequent are ``cut'' by
following (\ref{alpha-cut}) for every element in a fuzzy set
representing a consequent. In an intuitionistic MF, one can follow
the same procedure in order to obtain the $\alpha$-cut in the MF part,
but to obtain the $\alpha$-cut in the NMF, (\ref{nmf-alpha-cut}) must
be followed. In (\ref{nmf-alpha-cut}), the counterintuitive part is
that one has to find the corresponding $\nu$ for a given $\mu_{alpha}$.

\begin{equation}
  \label{alpha-cut}
  \alpha(\mu (x),\mu_{\alpha}) =
  \begin{cases}
    \mu (x), & \text{if}\ \mu (x) \leq \mu_{alpha}  \\
    \mu_{\alpha}, & \text{otherwise}
  \end{cases}
\end{equation}

\begin{equation}
  \label{nmf-alpha-cut}
  \alpha_{NMF}(\nu (x),\mu_{\alpha}) =
  \begin{cases}
    \nu (x), & \text{if}\ \nu (x) \geq \nu (\mu_{alpha})  \\
    \nu (\mu_{alpha}), & \text{otherwise}
  \end{cases}
\end{equation}

% How the coa is calculated (show formula and plot). How the formula can
% be contracted.

\begin{figure}[!t]
  \centering
  \includegraphics[width=2.5in]{alpha-cut}
  \caption{$\alpha$-cut of an Intuitionistic Fuzzy Set}
  \label{alpha-cut}
\end{figure}

\begin{figure}[!t]
  \centering
  \includegraphics[width=2.5in]{ifs-union}
  \caption{Union of Three $\alpha$-cut Intuitionistic Fuzzy Sets}
  \label{ifs-union}
\end{figure}

@@
